---
title: "2017 09 11 Coursera JNU Week 3 Assn"
author: "Brian Gue"
date: "September 11, 2017"
output:
  revealjs::revealjs_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
R Markdown Presentation & Plotly Plots
Brian Gue
Sept 11, 2017


## Data
The data is a subset of the ggplot2 sample diamonds dataset.
```{r diamonds,echo=TRUE}
library(ggplot2)
data(diamonds)
d <- diamonds[sample(nrow(diamonds), 50), ]
summary(d)
d
```

## Including Plots

Here's a plot generated by plotly.  With a few lines, we get hoverovers for both features of the dataset (prce, and carat). 

on the chart, both color and size indicate carat.
```{r plotsetup, echo=TRUE}
library(plotly)

p <- plot_ly(
  d, x = ~carat, y = ~price,
  # Hover text:
  text = ~paste("Price: ", price, '$<br>Cut:', cut),
  color = ~carat, size = ~carat
)
```

## The Plot
```{r plot, echo=FALSE}
p
```
The chart itself repeats one you can find in the plotly documentation, at https://plot.ly/r/line-and-scatter/ . 
